### 2014-06-09 paper/paper.tex
final version for tables 1 and 3. Letter for reviewers and diff pdf updated

The first point to check is if the different weight vectors affect the solutions obtained by MO-MCTS. Table~\ref{tab:weights} shows the results of executing the MO-MCTS controller during $30$ games in each one of the $10$ maps of the MO-PTSP, for every weight vector. It can be seen that the highest weight in $W$ leads, in most of the cases, to the best solution in that objective in the map.

\begin{table}[!t]
\begin{center}
%\begin{tabular}{|>{\centering\arraybackslash}m{0.65cm}|c|c|c|c|}
\begin{tabular}{|p{0.8cm}|p{2.2cm}|m{1.13cm}|m{1.13cm}|m{1.13cm}|}
\hline
\textbf{Map}  & \textbf{$W:(w_t, w_f, w_d)$} & \textbf{Time} &  \textbf{Fuel} & \textbf{Damage} \\ 
\hline
 \multirow{3}{*}{\textbf{Map 1}} & $(0.33,0.33,0.33)$ & $1654 \pm 7$ & $131 \pm 2$& $846 \pm 13$\\
 & $(0.1,0.3,0.6)$ & $1657 \pm 8$ & $130 \pm 2$ & \bm{$773 \pm 11$}\\
 & $(0.1,0.6,0.3)$ & $1681 \pm 11$ & $131 \pm 2$ & $837 \pm 15$\\
 & $(0.6,0.1,0.3)$ & $1649 \pm 8$ & $132 \pm 2$ & $833 \pm 13$\\
\hline
 \multirow{3}{*}{\textbf{Map 2}} & $(0.33,0.33,0.33)$ & $1409 \pm 7$ & $235 \pm 4$& $364 \pm 3$\\
 & $(0.1,0.3,0.6)$ & $1402 \pm 6$ & $236 \pm 5$ & \bm{$354 \pm 2$}\\
 & $(0.1,0.6,0.3)$ & $1416 \pm 8$ & \bm{$219 \pm 4$} & $360 \pm 3$\\
 & $(0.6,0.1,0.3)$ & $1396 \pm 8$ & $245 \pm 5$ & $361 \pm 2$\\
\hline
 \multirow{3}{*}{\textbf{Map 3}} & $(0.33,0.33,0.33)$ & $1373 \pm 6$ & $221 \pm 3$& $301 \pm 7$\\
 & $(0.1,0.3,0.6)$ & $1378 \pm 5$ & $211 \pm 3$ & \bm{$268 \pm 5$}\\
 & $(0.1,0.6,0.3)$ & $1385 \pm 6$ & \bm{$203 \pm 4$} & $291 \pm 7$\\
 & $(0.6,0.1,0.3)$ & \bm{$1363 \pm 4$} & $229 \pm 4$ & $285 \pm 7$\\
\hline
 \multirow{3}{*}{\textbf{Map 4}} & $(0.33,0.33,0.33)$ & $1383 \pm 6$ & $291 \pm 5$& $565 \pm 5$\\
 & $(0.1,0.3,0.6)$ & $1385 \pm 7$ & $304 \pm 4$ & \bm{$542 \pm 4$}\\
 & $(0.1,0.6,0.3)$ & $1423 \pm 6$ & \bm{$273 \pm 4$} & $583 \pm 5$\\
 & $(0.6,0.1,0.3)$ & $1388 \pm 6$ & $309 \pm 4$ & $559 \pm 5$\\
\hline
 \multirow{3}{*}{\textbf{Map 5}} & $(0.33,0.33,0.33)$ & $1405 \pm 7$ & $467 \pm 4$& $559 \pm 4$\\
 & $(0.1,0.3,0.6)$ & $1431 \pm 9$ & $447 \pm 4$ & $541 \pm 4$\\
 & $(0.1,0.6,0.3)$ & $1467 \pm 9$ & \bm{$411 \pm 5$} & $567 \pm 5$\\
 & $(0.6,0.1,0.3)$ & $1399 \pm 9$ & $469 \pm 4$ & $547 \pm 3$\\
\hline
 \multirow{3}{*}{\textbf{Map 6}} & $(0.33,0.33,0.33)$ & $1575 \pm 7$ & $549 \pm 5$& $303 \pm 4$\\
 & $(0.1,0.3,0.6)$ & $1626 \pm 9$ & $540 \pm 6$ & $286 \pm 5$\\
 & $(0.1,0.6,0.3)$ & $1703 \pm 11$ & \bm{$499 \pm 4$} & $316 \pm 7$\\
 & $(0.6,0.1,0.3)$ & $1571 \pm 7$ & $559 \pm 5$ & $294 \pm 4$\\
\hline
 \multirow{3}{*}{\textbf{Map 7}} & $(0.33,0.33,0.33)$ & $1434 \pm 5$ & $599 \pm 6$& $284 \pm 6$\\
 & $(0.1,0.3,0.6)$ & $1475 \pm 10$ & $602 \pm 5$ & \bm{$243 \pm 6$}\\
 & $(0.1,0.6,0.3)$ & $1489 \pm 12$ & \bm{$549 \pm 3$} & $264 \pm 6$\\
 & $(0.6,0.1,0.3)$ & \bm{$1407 \pm 8$} & $618 \pm 5$ & $270 \pm 6$\\
\hline
 \multirow{3}{*}{\textbf{Map 8}} & $(0.33,0.33,0.33)$ & $1761 \pm 9$ & $254 \pm 5$& $382 \pm 3$\\
 & $(0.1,0.3,0.6)$ & $1804 \pm 10$ & $269 \pm 4$ & \bm{$357 \pm 4$}\\
 & $(0.1,0.6,0.3)$ & $1826 \pm 10$ & \bm{$230 \pm 3$} & $392 \pm 7$\\
 & $(0.6,0.1,0.3)$ & \bm{$1732 \pm 9$} & $311 \pm 8$ & $379 \pm 6$\\
\hline
 \multirow{3}{*}{\textbf{Map 9}} & $(0.33,0.33,0.33)$ & $2501 \pm 14$ & $926 \pm 6$& $574 \pm 9$\\
 & $(0.1,0.3,0.6)$ & $2503 \pm 10$ & $921 \pm 10$ & \bm{$524 \pm 8$}\\
 & $(0.1,0.6,0.3)$ & $2641 \pm 14$ & \bm{$833 \pm 5$} & $574 \pm 14$\\
 & $(0.6,0.1,0.3)$ & \bm{$2470 \pm 9$} & $956 \pm 5$ & $573 \pm 8$\\
\hline
 \multirow{3}{*}{\textbf{Map 10}} & $(0.33,0.33,0.33)$ & $1430 \pm 8$ & $630 \pm 4$& $205 \pm 2$\\
 & $(0.1,0.3,0.6)$ & $1493 \pm 13$ & $615 \pm 4$ & $209 \pm 2$\\
 & $(0.1,0.6,0.3)$ & $1542 \pm 10$ & \bm{$554 \pm 4$} & $229 \pm 5$\\
 & $(0.6,0.1,0.3)$ & \bm{$1378 \pm 5$} & $663 \pm 6$ & $202 \pm 4$\\
\hline
\end{tabular}
\caption{MO-PTSP results with different weight vectors. Values in bold indicate the best results on each map, when they are separated at least by $2$ standard errors from the others.}
\label{tab:weights}
\end{center}
\end{table}

>>>>

The first point to check is if the different weight vectors affect the solutions obtained by MO-MCTS. Table~\ref{tab:weights} shows the results of executing the MO-MCTS controller during $30$ games in each one of the $10$ maps of the MO-PTSP, for every weight vector. This table includes the averages and standard errors obtained. Results in bold are those with an independent t-test p-value smaller than $0.01$, comparing the results of the objective with the highest weight with the result from the default weight vector $W_1 = (0.33,0.33,0.33)$ in the same map. It can be seen that the highest weight in $W$ leads, in most of the cases, to the best solution in that objective in the map.

\begin{table}[!t]
\begin{center}
%\begin{tabular}{|>{\centering\arraybackslash}m{0.65cm}|c|c|c|c|}
\begin{tabular}{|p{0.8cm}|p{2.2cm}|m{1.2cm}|m{1.13cm}|m{1.13cm}|}
\hline
\textbf{Map}  & \textbf{$W:(w_t, w_f, w_d)$} & \textbf{Time} &  \textbf{Fuel} & \textbf{Damage} \\ 
\hline
 \multirow{3}{*}{\textbf{Map 1}} & $(0.33,0.33,0.33)$ & $1654$ $(7)$ & $131$ $(2)$& $846$ $(13)$\\
 & $(0.1,0.3,0.6)$ & $1657$ $(8)$ & $130$ $(2)$ & \bm{$773$ $(11)$}\\
 & $(0.1,0.6,0.3)$ & $1681$ $(11)$ & $131$ $(2)$ & $837$ $(15)$\\
 & $(0.6,0.1,0.3)$ & $1649$ $(8)$ & $132$ $(2)$ & $833$ $(13)$\\
\hline
 \multirow{3}{*}{\textbf{Map 2}} & $(0.33,0.33,0.33)$ & $1409$ $(7)$ & $235$ $(4)$& $364$ $(3)$\\
 & $(0.1,0.3,0.6)$ & $1402$ $(6)$ & $236$ $(5)$ & \bm{$354$ $(2)$}\\
 & $(0.1,0.6,0.3)$ & $1416$ $(8)$ & \bm{$219$ $(4)$} & $360$ $(3)$\\
 & $(0.6,0.1,0.3)$ & $1396$ $(8)$ & $245$ $(5)$ & $361$ $(2)$\\
\hline
 \multirow{3}{*}{\textbf{Map 3}} & $(0.33,0.33,0.33)$ & $1373$ $(6)$ & $221$ $(3)$& $301$ $(7)$\\
 & $(0.1,0.3,0.6)$ & $1378$ $(5)$ & $211$ $(3)$ & \bm{$268$ $(5)$}\\
 & $(0.1,0.6,0.3)$ & $1385$ $(6)$ & \bm{$203$ $(4)$} & $291$ $(7)$\\
 & $(0.6,0.1,0.3)$ & $1363$ $(4)$ & $229$ $(4)$ & $285$ $(7)$\\
\hline
 \multirow{3}{*}{\textbf{Map 4}} & $(0.33,0.33,0.33)$ & $1383$ $(6)$ & $291$ $(5)$& $565$ $(5)$\\
 & $(0.1,0.3,0.6)$ & $1385$ $(7)$ & $304$ $(4)$ & \bm{$542$ $(4)$}\\
 & $(0.1,0.6,0.3)$ & $1423$ $(6)$ & \bm{$273$ $(4)$} & $583$ $(5)$\\
 & $(0.6,0.1,0.3)$ & $1388$ $(6)$ & $309$ $(4)$ & $559$ $(5)$\\
\hline
 \multirow{3}{*}{\textbf{Map 5}} & $(0.33,0.33,0.33)$ & $1405$ $(7)$ & $467$ $(4)$& $559$ $(4)$\\
 & $(0.1,0.3,0.6)$ & $1431$ $(9)$ & $447$ $(4)$ & \bm{$541$ $(4)$}\\
 & $(0.1,0.6,0.3)$ & $1467$ $(9)$ & \bm{$411$ $(5)$} & $567$ $(5)$\\
 & $(0.6,0.1,0.3)$ & $1399$ $(9)$ & $469$ $(4)$ & $547$ $(3)$\\
\hline
 \multirow{3}{*}{\textbf{Map 6}} & $(0.33,0.33,0.33)$ & $1575$ $(7)$ & $549$ $(5)$& $303$ $(4)$\\
 & $(0.1,0.3,0.6)$ & $1626$ $(9)$ & $540$ $(6)$ & $286$ $(5)$\\
 & $(0.1,0.6,0.3)$ & $1703$ $(11)$ & \bm{$499$ $(4)$} & $316$ $(7)$\\
 & $(0.6,0.1,0.3)$ & $1571$ $(7)$ & $559$ $(5)$ & $294$ $(4)$\\
\hline
 \multirow{3}{*}{\textbf{Map 7}} & $(0.33,0.33,0.33)$ & $1434$ $(5)$ & $599$ $(6)$& $284$ $(6)$\\
 & $(0.1,0.3,0.6)$ & $1475$ $(10)$ & $602$ $(5)$ & $243$ $(6)$\\
 & $(0.1,0.6,0.3)$ & $1489$ $(12)$ & \bm{$549$ $(3)$} & $264$ $(6)$\\
 & $(0.6,0.1,0.3)$ & \bm{$1407$ $(8)$} & $618$ $(5)$ & $270$ $(6)$\\
\hline
 \multirow{3}{*}{\textbf{Map 8}} & $(0.33,0.33,0.33)$ & $1761$ $(9)$ & $254$ $(5)$& $382$ $(3)$\\
 & $(0.1,0.3,0.6)$ & $1804$ $(10)$ & $269$ $(4)$ & \bm{$357$ $(4)$}\\
 & $(0.1,0.6,0.3)$ & $1826$ $(10)$ & $230$ $(3)$ & $392$ $(7)$\\
 & $(0.6,0.1,0.3)$ & $1732$ $(9)$ & $311$ $(8)$ & $379$ $(6)$\\
\hline
 \multirow{3}{*}{\textbf{Map 9}} & $(0.33,0.33,0.33)$ & $2501$ $(14)$ & $926$ $(6)$& $574$ $(9)$\\
 & $(0.1,0.3,0.6)$ & $2503$ $(10)$ & $921$ $(10)$ & \bm{$524$ $(8)$}\\
 & $(0.1,0.6,0.3)$ & $2641$ $(14)$ & \bm{$833$ $(5)$} & $574$ $(14)$\\
 & $(0.6,0.1,0.3)$ & $2470$ $(9)$ & $956$ $(5)$ & $573$ $(8)$\\
\hline
 \multirow{3}{*}{\textbf{Map 10}} & $(0.33,0.33,0.33)$ & $1430$ $(8)$ & $630$ $(4)$& $205$ $(2)$\\
 & $(0.1,0.3,0.6)$ & $1493$ $(13)$ & $615$ $(4)$ & $209$ $(2)$\\
 & $(0.1,0.6,0.3)$ & $1542$ $(10)$ & \bm{$554$ $(4)$} & $229$ $(5)$\\
 & $(0.6,0.1,0.3)$ & \bm{$1378$ $(5)$} & $663$ $(6)$ & $202$ $(4)$\\
\hline
\end{tabular}
\caption{MO-PTSP averages (plus standard error) with different weight vectors. Results in bold obtained an independent t-test p-value $<0.01$.}
\label{tab:weights}
\end{center}
\end{table}

%\begin{table}[!t]
%\begin{center}
%%\begin{tabular}{|>{\centering\arraybackslash}m{0.65cm}|c|c|c|c|}
%\bgroup
%%\def\arraystretch{0.9}%  1 is the default, change whatever you need
%\renewcommand\tabcolsep{5pt}
%\begin{tabular}{|p{0.9cm}|p{0.5cm}|m{1.9cm}|m{1.75cm}|m{1.75cm}|}
%\hline
%\textbf{Map}  & \textbf{$W$} & \textbf{Time} &  \textbf{Fuel} & \textbf{Damage} \\ 
%\hline
% \multirow{3}{*}{\textbf{Map 1}} & $W_1$ & $1654$ & $131$& $846$\\
% & $W_2$ & $1657$ & $130$ & \textbf{773} \bm{$(<0.01)$}\\
% & $W_3$ & $1681$ & $131$ $(1.0)$ & $837$\\
% & $W_4$ & $1649$ $(0.63)$ & $132$ & $833$\\
%\hline
% \multirow{3}{*}{\textbf{Map 2}} & $W_1$ & $1409$ & $235$& $364$\\
% & $W_2$ & $1402$ & $236$ & \textbf{354} \bm{$(<0.01)$}\\
% & $W_3$ & $1416$ & \textbf{219} \bm{$(<0.01)$} & $360$\\
% & $W_4$ & $1396$ $(0.22)$ & $245$ & $361$\\
%\hline
% \multirow{3}{*}{\textbf{Map 3}} & $W_1$ & $1373$ & $221$& $301$\\
% & $W_2$ & $1378$ & $211$ & \textbf{268} \bm{$(<0.01)$}\\
% & $W_3$ & $1385$ & \textbf{203} \bm{$(<0.01)$} & $291$\\
% & $W_4$ & $1363$ $(0.17)$ & $229$ & $285$\\
%\hline
% \multirow{3}{*}{\textbf{Map 4}} & $W_1$ & $1383$ & $291$& $565$\\
% & $W_2$ & $1385$ & $304$ & \textbf{542} \bm{$(<0.01)$}\\
% & $W_3$ & $1423 $ & \textbf{273} \bm{$(<0.01)$} & $583$\\
% & $W_4$ & $1388$ $(0.55)$ & $309$ & $559$\\
%\hline
% \multirow{3}{*}{\textbf{Map 5}} & $W_1$ & $1405$ & $467$& $559$\\
% & $W_2$ & $1431$ & $447$ & \textbf{541} \bm{$(<0.01)$}\\
% & $W_3$ & $1467$ & \textbf{411} \bm{$(<0.01)$} & $567$\\
% & $W_4$ & $1399$ $(0.60)$ & $469$ & $547$\\
%\hline
% \multirow{3}{*}{\textbf{Map 6}} & $W_1$ & $1575$ & $549$& $303$\\
% & $W_2$ & $1626$ & $540$ & \textbf{286} \bm{$(0.01)$}\\
% & $W_3$ & $1703$ & \textbf{499} \bm{$(<0.01)$} & $316$\\
% & $W_4$ & $1571$ $(0.68)$ & $559$ & $294$\\
%\hline
% \multirow{3}{*}{\textbf{Map 7}} & $W_1$ & $1434$ & $599$& $284$\\
% & $W_2$ & $1475$ & $602$ & \textbf{243} \bm{$(0.01)$}\\
% & $W_3$ & $1489$ & \textbf{549} \bm{$(<0.01)$} & $264$\\
% & $W_4$ & \textbf{1407} \bm{$(<0.01)$} & $618$ & $270$\\
%\hline
% \multirow{3}{*}{\textbf{Map 8}} & $W_1$ & $1761 $ & $254$& $382$\\
% & $W_2$ & $1804$ & $269$ & \textbf{357} \bm{$(<0.01)$}\\
% & $W_3$ & $1826$ & 230 \bm{$(<0.01)$} & $392$\\
% & $W_4$ & \textbf{1732} \bm{$(0.02)$} & $311$ & $379$\\
%\hline
% \multirow{3}{*}{\textbf{Map 9}} & $W_1$ & $2501$ & $926$& $574$\\
% & $W_2$ & $2503$ & $921$ & \textbf{524} \bm{$(<0.01)$}\\
% & $W_3$ & $2641$ & \textbf{833} \bm{$(<0.01)$} & $574$\\
% & $W_4$ & $2470$ $(0.06)$ & $956$ & $573$\\
%\hline
% \multirow{3}{*}{\textbf{Map 10}} & $W_1$ & $1430$ & $630$& $205$\\
% & $W_2$ & $1493$ & $615$ & $209$ $(0.16)$\\
% & $W_3$ & $1542$ & \textbf{554} \bm{$(<0.01)$} & $229$\\
% & $W_4$ & \textbf{1378} \bm{$(<0.01)$} & $663$ & $202$\\
%\hline
%\end{tabular}
%\egroup
%\caption{MO-PTSP averages with different weight vectors. Includes p-values for the objective with the highest weight. Results in bold are statistically significant (p-value $<0.05$).}
%\label{tab:weights}
%\end{center}
%\end{table}

%\begin{table}[!t]
%\begin{center}
%%\begin{tabular}{|>{\centering\arraybackslash}m{0.65cm}|c|c|c|c|}
%\bgroup
%%\def\arraystretch{0.9}%  1 is the default, change whatever you need
%\renewcommand\tabcolsep{5pt}
%\begin{tabular}{|p{0.9cm}|p{0.5cm}|m{1.9cm}|m{1.75cm}|m{1.75cm}|}
%\hline
%\textbf{Map}  & \textbf{$W$} & \textbf{Time} &  \textbf{Fuel} & \textbf{Damage} \\ 
%\hline
% \multirow{3}{*}{\textbf{Map 1}} & $W_1$ & $1654$ & $131$& $846$\\
% & $W_2$ & $1657$ & $130$ & \textbf{773} \bm{$(<0.01)$}\\
% & $W_3$ & $1681$ & \textbf{131} $(0.72)$ & $837$\\
% & $W_4$ & \textbf{1649} $(0.63)$ & $132$ & $833$\\
%\hline
% \multirow{3}{*}{\textbf{Map 2}} & $W_1$ & $1409$ & $235$& $364$\\
% & $W_2$ & $1402$ & $236$ & $354$ $(0.1)$\\
% & $W_3$ & $1416$ & \textbf{219} \bm{$(0.01)$} & $360$\\
% & $W_4$ & \textbf{1396} $(0.55)$ & $245$ & $361$\\
%\hline
% \multirow{3}{*}{\textbf{Map 3}} & $W_1$ & $1373$ & $221$& $301$\\
% & $W_2$ & $1378$ & $211$ & \textbf{268} $(0.053)$\\
% & $W_3$ & $1385$ & \textbf{203} $(0.11)$ & $291$\\
% & $W_4$ & \textbf{1363} $(0.17)$ & $229$ & $285$\\
%\hline
% \multirow{3}{*}{\textbf{Map 4}} & $W_1$ & \textbf{1383} & $291$& $565$\\
% & $W_2$ & $1385$ & $304$ & \textbf{542} \bm{$(0.01)$}\\
% & $W_3$ & $1423 $ & \textbf{273} \bm{$(0.01)$} & $583$\\
% & $W_4$ & $1388$ $(0.74)$ & $309$ & $559$\\
%\hline
% \multirow{3}{*}{\textbf{Map 5}} & $W_1$ & $1405$ & $467$& $559$\\
% & $W_2$ & $1431$ & $447$ & \textbf{541} $(0.23)$\\
% & $W_3$ & $1467$ & \textbf{411} \bm{$(<0.01)$} & $567$\\
% & $W_4$ & \textbf{1399} $(0.60)$ & $469$ & $547$\\
%\hline
% \multirow{3}{*}{\textbf{Map 6}} & $W_1$ & $1575$ & $549$& $303$\\
% & $W_2$ & $1626$ & $540$ & \textbf{286} $(0.21)$\\
% & $W_3$ & $1703$ & \textbf{499} \bm{$(<0.01)$} & $316$\\
% & $W_4$ & \textbf{1571} $(0.68)$ & $559$ & $294$\\
%\hline
% \multirow{3}{*}{\textbf{Map 7}} & $W_1$ & $1434$ & $599$& $284$\\
% & $W_2$ & $1475$ & $602$ & \textbf{243} \bm{$(0.01)$}\\
% & $W_3$ & $1489$ & \textbf{549} \bm{$(<0.01)$} & $264$\\
% & $W_4$ & \textbf{1407} \bm{$(0.01)$} & $618$ & $270$\\
%\hline
% \multirow{3}{*}{\textbf{Map 8}} & $W_1$ & $1761 $ & $254$& $382$\\
% & $W_2$ & $1804$ & $269$ & 357 \bm{$(<0.01)$}\\
% & $W_3$ & $1826$ & 230 \bm{$(<0.01)$} & $392$\\
% & $W_4$ & \textbf{1732} \bm{$(0.02)$} & $311$ & $379$\\
%\hline
% \multirow{3}{*}{\textbf{Map 9}} & $W_1$ & $2501$ & $926$& $574$\\
% & $W_2$ & $2503$ & $921$ & \textbf{524} \bm{$(<0.01)$}\\
% & $W_3$ & $2641$ & \textbf{833} \bm{$(<0.01)$} & $574$\\
% & $W_4$ & \textbf{2470} $(0.06)$ & $956$ & $573$\\
%\hline
% \multirow{3}{*}{\textbf{Map 10}} & $W_1$ & $1430$ & $630$& $205$\\
% & $W_2$ & $1493$ & $615$ & \textbf{209} $(0.16)$\\
% & $W_3$ & $1542$ & \textbf{554} \bm{$(0.00)$} & $229$\\
% & $W_4$ & \textbf{1378} \bm{$(<0.01)$} & $663$ & $202$\\
%\hline
%\end{tabular}
%\egroup
%\caption{MO-PTSP results with different weight vectors. Values in bold indicate the best results on each map, when they are separated at least by $2$ standard errors from the others.}
%\label{tab:weights}
%\end{center}
%\end{table}
